A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$

### 2025-04-06 paper_v02/article.tex
elapsed time images

Figure \ref{fig:elapsed_tws_04
} shows the elapsed computation time difference from the Basic to the optimized version of the algorithm increases as the time scale increases. If the test was conducted with a bigger time series, and with larger time scales the difference would be even more significant.

>>>>

Figure \ref{fig:elapsed_tws_04} shows the elapsed computation time difference from the Basic to the optimized version of the algorithm increases as the time scale increases. If the test was conducted with a bigger time series, and with larger time scales the difference would be even more significant.
